The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-11 rational.tex
_

\paragraph*{Geometry of Interaction (GoI.}
This geometry was developed by Girard~\cite{girard1989geometry} as part of
the development of linear logic. It was given a computational interpretation
by Abramsky and Jagadeesan~\cite{Abramsky:1994:NFG:184662.184664}, and was
developed into a reversible model of computing by
Mackie~\cite{Mackie2011,DBLP:conf/popl/Mackie95}. Preliminary investigations
suggest that many of the GoI machine constructions can be simulated in
{{langRevEE}} by treating Mackie's bi-directional wires as pairs of wires in
{{langRevEE}} and replacing the machine's global state with a typed value on
the wire that captures the appropriate state. This connection is exciting
because when viewed through a Curry-Howard lens it suggests that the logical
interpretation of {{langRevEE}} would be a linear-like logic with a notion of
resource preservation and with a natural computational interpretation.

>>>>

\paragraph*{Geometry of Interaction (GoI).}
Geometry of Interaction was developed by Girard~\cite{girard1989geometry} as part of
the development of linear logic. It was given a computational interpretation
by Abramsky and Jagadeesan~\cite{Abramsky:1994:NFG:184662.184664}, and was
developed into a reversible model of computing by
Mackie~\cite{Mackie2011,DBLP:conf/popl/Mackie95}. Preliminary investigations
suggest that many of the GoI machine constructions can be simulated in
{{langRevEE}} by treating Mackie's bi-directional wires as pairs of wires in
{{langRevEE}} and replacing the machine's global state with a typed value on
the wire that captures the appropriate state. This connection is exciting
because when viewed through a Curry-Howard lens it suggests that the logical
interpretation of {{langRevEE}} would be a linear-like logic with a notion of
resource preservation and with a natural computational interpretation.
